Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-13 paper.tex
Tweak CFT wake studies in introduction

The wake of a cross-flow turbine in the dynamic stall regime has been studied
via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and with
particle image velocimetry (PIV) by Fujisawa and Shibuya \cite{Fujisawa2001}.
However, both of these studies were performed at very low Reynolds
numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine in a wind
tunnel using stereo PIV at an approximate blade chord Reynolds number $Re_c =
1.7 \times 10^5$; very close to the $Re$-independent state reported in
\cite{Bachant2014}, where 2-D near-wake profiles were measured for a high
solidity cross-flow turbine at optimal tip speed ratio.

>>>>

The wake of a 2-D cross-flow turbine in the dynamic stall regime has been
studied via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and
in 3-D with particle image velocimetry (PIV) by Fujisawa and Shibuya
\cite{Fujisawa2001}. However, both of these studies were performed at very low
Reynolds numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine at optimal
tip speed ratio in a wind tunnel using stereo PIV at an approximate blade chord
Reynolds number $Re_c = 1.7 \times 10^5$; very close to the $Re$-independence
criteria reported in \cite{Bachant2014}, though it was not confirmed if this was
indeed a $Re$-independent state. These studies motivate the systematic
investigation of scale effects undertaken here.
